Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-25 analysis/paper/paper.Rmd
Clean up legend for figure 4

a <- plot(m_g1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.box.spacing = unit(40, "pt")
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "grey70") +
  ggtitle("Code") +
  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)

b <-
  plot(m_g2_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.box.spacing = unit(40, "pt")
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "black") +
  ggtitle("Data") +
  coord_cartesian(ylim = c(0.8, 20), expand = FALSE)

>>>>

a <- plot(m_g1_eq,
          show_labels = TRUE,
          rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.box.spacing = unit(40, "pt"),
    legend.position = "bottom",
    legend.justification = "right",
    legend.margin = margin(r = -5)
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "grey70") +
  ggtitle("Code") +
  coord_cartesian(ylim = c(0.9, 6), expand = FALSE)

b <-
  plot(m_g2_eq,
       show_labels = TRUE,
       rope_color = "grey10") +
  theme(
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.box.spacing = unit(40, "pt"),
    legend.position = "bottom",
    legend.justification = "left",
    legend.margin = margin(l = -5)
  ) +
  xlim(-0.3, 0.7) +
  scale_fill_manual(values = "black") +
  ggtitle("Data") +
  coord_cartesian(ylim = c(0.8, 20), expand = FALSE)
